---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# hellozig

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of `hellozig` is to play with R and [zig](https://ziglang.org/).

> Zig is a general-purpose programming language designed for robustness, optimality, and maintainability.

## Installation

You need to [install](https://github.com/ziglang/zig/wiki/Install-Zig-from-a-Package-Manager) the zig compiler `zig` to use this package.

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(hellozig)

zig_add(10, 20)
```

```{r}
zig_fibonacci(12)
```

The actual zig code looks like this:

```rust
export fn zig_add(a: i32, b: i32) i32 {
    return a + b;
}

export fn zig_fibonacci(n: i64) i64 {
  if (n < 2) {
    return n;
  }
  return zig_fibonacci(n - 2) + zig_fibonacci(n - 1);
}
```

## References

* [hellorust](https://github.com/r-rust/hellorust) - uses the same approach.
* [ziglang](https://ziglang.org/)
